Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/spin-cring.tex
reinstate previous changes

\sssec{Idea of proof:} The construction of the $y_{i,e_i}$ in Part (a) uses Riemann--Roch and condition ~\ref{custom:Ad-iii}. The inequality in Part (a) follows from the fact that $L$ is similar to $L'$, but with some of the $e_i$ incremented by $2$. Part (b) follows because the sublattice spanned by $y_{i,e_i}$ and $y_{i, e_i'}$ has determinant $1$ for $i \in J,$ so the generators in Part (a) generate all of $R_\halfcan$ over $R_{\halfcan'}$. To check part (c) we construct relations between the generators of $R_{\halfcan}$ over $R_{\halfcan'}$. We note that an element lies in $R_{\halfcan'}$ if and only if its pole order at $P_i$ for $i \in J$ is not too large, and use Lemma ~\ref{lem:admissible_inequality} to check this bound. Part (d) follows fairly easily from the definition of admissibility.

>>>>

\sssec*{Idea of proof:}
The construction of the $y_{i, e_i}$ in Part (a) uses Riemann--Roch
and condition ~\ref{custom:Ad-iii}. The inequality in Part (a)
follows from the fact that $\halfcan$ is similar to $\halfcan'$,
but with some of the $e_i$ incremented by $2$. Part (b) follows
because the sub-lattice spanned by $y_{i, e_i}$ and $y_{i, e_i'}$
has determinant $1$ for $i \in J$, so the generators in Part (a)
generate all of $R_\halfcan$ over $R_{\halfcan'}$. To check part (c),
we construct relations between the generators of $R_{\halfcan}$
over $R_{\halfcan'}$: we note that an element lies in $R_{\halfcan'}$
if and only if its pole order at $P_i$ for $i \in J$ is not too
large, and use Lemma ~\ref{lem:admissible_inequality} to bound pole
orders. Part (d) follows fairly easily from the definition of
admissibility.
